%------------------------------------------------------
% My Resume in LaTeX 
% Author: Alireza Hanifi
% Inspired by:  
% https://github.com/sb2nov/resume &
% https://github.com/posquit0/Awesome-CV
%------------------------------------------------------

\documentclass[11pt, a4paper]{article}

% Packages
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{datetime}
\input{glyphtounicode}

% Helper command to format month and year
\newdateformat{monthyear}{\THEYEAR~\monthname[\THEMONTH]}

% Page style
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot[C]{
    \begin{tabularx}{\textwidth}{@{}lXr@{}}
        \footnotesize \monthyear\today & \centering\footnotesize Alireza Hanifi . Résumé & \footnotesize \thepage
    \end{tabularx}
}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.0in}

% URL style
\urlstyle{same}

% Section Formatting
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure machine readability of PDF
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.99\textwidth}{@{\extracolsep{\fill}}lr}
        \textbf{#1} & #2 \\
        \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

% Custom lists
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}


% Heading
\begin{center}
    {\Huge \textbf{Alireza Hanifi}} \\[1ex]
    {\Large \textbf{Data Engineer $|$ BI Developer}} \\[1ex]
    Tehran, Iran $|$
    \href{tel:+989383385818}{(+98) 938-338-5818} $|$
    \href{mailto:a.hanifi1375@gmail.com}{a.hanifi1375@gmail.com} \\[.5ex]
    \href{https://www.linkedin.com/in/Alireza-Hanifi}{linkedin.com/in/Alireza-Hanifi} $|$
    \href{https://github.com/AlirezaHanifi}{github.com/AlirezaHanifi} $|$
    \href{https://AlirezaHanifi.github.io/}{AlirezaHanifi.github.io}
\end{center}

% About Me
\section{About Me}
I'm a BI Developer with more than 2 years of experience, dedicated to leveraging data to solve business challenges. As I progress in the data realm, I aim to shift into a Data Engineer role. Building data pipelines and managing substantial datasets has motivated me to pursue complex data infrastructure tasks.

% Experience
\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
        {\href{https://blubank.sb24.ir/}{blu Bank}}{Tehran, Iran}
        {Business Intelligence Developer}{Jan 2024 - Present}
        \resumeItemListStart
            \resumeItem{Built and improved Airflow pipelines (20+ DAGs, 40+ tables) and implemented a star schema for efficient data analysis.}
            \resumeItem{Optimized PostgreSQL performance with indexing and storage strategies, reducing table sizes by up to 80\% and improving query response times by up to 50\%.}
            \resumeItem{Developed Metabase dashboards and defined key metrics, providing product managers with actionable insights for the Box and PFM sections, leading to nearly 100\% new user acquisition for these features within 3 months.}
            \resumeItem{Enhanced marketing campaign effectiveness through pre-launch validation, in-campaign monitoring, and post-campaign analysis, resulting in a 2\% increase in deposits with the round-up campaign.}
            \resumeItem{Collaborated effectively with cross-functional teams to ensure alignment on data requirements and interpretations, fostering data-driven decision-making across departments.}
        \resumeItemListEnd
        \vspace{0.5\baselineskip}
        
    \resumeSubheading
        {\href{https://www.emofid.com/}{Mofid Securities}}{Tehran, Iran}
        {Business Intelligence Analyst}{Sep 2022 - Dec 2023 (1 yr 4 mos)}
        \resumeItemListStart
            \resumeItem{Revamped and implemented data models and algorithms to clean, transform, and validate data, reducing daily workload by up to 2 hours.}
            \resumeItem{Designed and managed 50+ dashboards using tools like Tableau and Grafana, effectively communicating complex data insights.}
            \resumeItem{Partnered with cross-functional teams to define data needs and interpret results, facilitating data-driven decision-making.}
        \resumeItemListEnd
        \vspace{0.5\baselineskip}

    \resumeSubheading
        {\href{https://mofidacademy.com//}{Mofid Academy}}{Tehran, Iran}
        {Finance Intern}{Jul 2022 - Sep 2022 (3 mos)}
        \resumeItemListStart
            \resumeItem{Mastered Tehran Stock Exchange and trading tools, and improved proficiency in CRM skills.}
            \resumeItem{Contributed to research projects applying AI in finance and conducted data analysis for investment strategies.}
            \resumeItem{Developed strong analytical abilities and efficient scheduling through research and analysis of financial data, supporting investment strategy development.}
        \resumeItemListEnd
\resumeSubHeadingListEnd

% Education
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
        {\href{https://english.iut.ac.ir/}{Isfahan University of Technology}}{Isfahan, Iran}
        {B.Sc. in Mechanical Engineering}{Sep 2015 - Feb 2020}
\resumeSubHeadingListEnd

% Technical Skills
\section{Technical Skills}
\resumeSubHeadingListStart
    \resumeItem{\textbf{Languages}: Python (FastAPI, Matplotlib, NumPy, Pandas, Polars, Seaborn), SQL, Bash}
    \resumeItem{\textbf{Data Technologies}: Airflow, Spark, Kafka, PostgreSQL, Oracle, ClickHouse, MongoDB, Minio}
    \resumeItem{\textbf{Data Engineering}: ETL, Data Modeling and Design, Performance Tuning}
    \resumeItem{\textbf{Tools}: Docker, Git, Grafana, Tableau, Confluence, Jira, Trello}
    \resumeItem{\textbf{Additional}: Machine Learning, Data Analysis and Visualization, Reporting}
    \resumeItem{\textbf{Languages}: English (Fluent), Persian (Native)}
\resumeSubHeadingListEnd

% Courses
\section{Courses}
\resumeSubHeadingListStart
    \resumeItem{Digital Product Management (Bozhan)}
    \resumeItem{Deep Learning Specialization by Andrew Ng (Coursera)}{\href{https://www.coursera.org/account/accomplishments/specialization/EN3BD5D7X97H}{[Certified]}}
    \resumeItem{Machine Learning with Python by Jadi (Maktabkhooneh)}{\href{https://maktabkhooneh.org/certificates/MK-KVBCQB/}{[Certified]}}
    \resumeItem{SQL for Data Science (Coursera)}{\href{https://www.coursera.org/account/accomplishments/verify/TLPV567X6MVR}{[Certified]}}
\resumeSubHeadingListEnd

\end{document}